Speeding up decimal multiplication

### 2020-11-23 paper/paper.tex
Update

\begin{enumerate}
  \item \textbf{Improve cache utilization}.
    \begin{enumerate}
      \item Use breadth-first ordering, perhaps using explicit recursion.
            This can be beneficial even considering the function call overhead,
            as it leads to better cache utilization~\cite{fftw}.
      \item Explore what~\cite{gmp_paper} call the ``Belgian approach''; see~\cite{belgian}.
      \item Explore using higher-radix transforms (raidx-4, radix-8, etc).
            Note that radix-4 is beneficial for complex FFT because,
            for a standard representation by a pair of floating-point values,
            multiplication by $i$ or $-i$ can be done significantly faster than normal
            multiplication; but finite fields of integers modulo $p$ with standard representation
            lack this property.
            Nevertheless, higher-radix transforms might be of service because they have better cache
            locality~\cite{fftw}.
    \end{enumerate}
  \item \textbf{Additional shenanigans}.
    \begin{enumerate}
      \item It is suggested in \cite{shenanigans, mont_sp} to use primes $p$ such that $p < \mu/4.$
          Then, the Montgomery multiplication can be implemented in such a way that if the inputs
          are in $[0; 2p-1],$ then the outputs are also in $[0; 2p-1],$ and no final conditional
          subtraction is performed.
      \item It is stated in~\cite{shenanigans_presentation} that we could benefit from
          higher-radix transforms by further eliminating reductions from the butterflies.
      \item Explore signed Montgomery reduction, as defined in~\cite{signed_montgomery}.
    \end{enumerate}
  \item \textbf{Smooth the stairs}, possibly utilizing ideas from~\cite{smooth_the_stairs}.
        Currently, we can only perform transforms of lengths $2^k$ and $3 \cdot 2^k.$
        It would be nice to be able to perform transforms of lengths that are in-between.
\end{enumerate}

>>>>

\begin{enumerate}
  \item \textbf{Improve cache utilization}.
    \begin{enumerate}
      \item Use breadth-first ordering, perhaps using explicit recursion.
            This can be beneficial even considering the function call overhead,
            as it leads to better cache utilization~\cite{fftw}.
      \item Explore what~\cite{gmp_paper} calls the ``Belgian approach''; see~\cite{belgian}.
      \item Explore using higher-radix transforms (raidx-4, radix-8, etc).
            Note that radix-4 is beneficial for complex FFT because,
            for a standard representation by a pair of floating-point values,
            multiplication by $i$ or $-i$ can be done significantly faster than normal
            multiplication; but finite fields of integers modulo $p$ with standard representation
            lack this property.
            Nevertheless, higher-radix transforms might be of service because they have better cache
            locality~\cite{fftw}.
    \end{enumerate}
  \item \textbf{Additional shenanigans}.
    \begin{enumerate}
      \item It is suggested in \cite{shenanigans, mont_sp} that we use primes $p$ such that $p < \mu/4.$
          Then, the Montgomery multiplication can be implemented in such a way that if the inputs
          are in $[0; 2p-1],$ then the outputs are also in $[0; 2p-1],$ and no final conditional
          subtraction is performed.
      \item It is stated in~\cite{shenanigans_presentation} that we could benefit from
          higher-radix transforms by further eliminating reductions from the butterflies.
      \item Explore signed Montgomery reduction, as defined in~\cite{signed_montgomery}.
    \end{enumerate}
  \item \textbf{Smooth the stairs}, possibly utilizing ideas from~\cite{smooth_the_stairs}.
        Currently, we can only perform transforms of lengths $2^k$ and $3 \cdot 2^k.$
        It would be nice to be able to perform transforms of lengths that are in-between.
\end{enumerate}
